---
title: "Practice7.4"
author: "Ethan Wang"
date: "2022-11-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE,include=F}
library(tidyverse)
```
## I create my.t.test for my customized t-test function.
```{r, echo=TRUE}
my.t.test <- function(x,y){ #this function can only be used to run independent t-test, and assume with equal variance
  #list the null hypothesis and alternative hypothesis of t-test
  cat(" ","H0:The true difference between these group means is zero.","\n"," Ha:The true difference is different from zero.","\n")
  if (is.character(y) == T) { #if one of the object contains the information of two groups, use pivot_wider() first to organize values into two groups
    xy_df <- data.frame(x,y) 
    xy_df_wide <- xy_df%>%
      group_by(y)%>%
      mutate(row = row_number())%>%
      pivot_wider(names_from = y, values_from = x)%>%
      select(-row)
    xy_df_wide <- as.data.frame(xy_df_wide) #revert it into data frame
    mean_1 <- mean(xy_df_wide[,1])
    mean_2 <- mean(xy_df_wide[,2])
    n1 <- length(xy_df_wide[,1])
    n2 <- length(xy_df_wide[,2])
    var_1 <- var(xy_df_wide[,1])
    var_2 <- var(xy_df_wide[,2])
    df <- (n1-1)+(n2-1)
    t <- (mean_1-mean_2)/sqrt((var_1/n1)+(var_2/n2)) #the formula of independent t-test
    if(t>0){
      pvalue <- pt(t,df,lower.tail = F)*2 #calculate p-value
    }else{
      pvalue <- pt(t,df)*2
    }
    if(pvalue < 0.05){
      cat("  t=",round(t,4)," ","df=",df," ","p-value=",round(pvalue,4),"\n"," Reject H0.")
    }else{
      cat("  t=",round(t,4)," ","df=",df," ","p-value=",round(pvalue,4),"\n"," Not reject H0")
    }
  }else{ #two objects contain values of two groups respectively
    mean_x <- mean(x)
    mean_y <- mean(y)
    var_x <- var(x)
    var_y <- var(y)
    nx <- length(x)
    ny <- length(y)
    df <- (nx-1)+(ny-1)
    t <- (mean_x-mean_y)/sqrt((var_x/nx)+(var_y/ny))
    if(t>0){
      pvalue <- pt(t,df,lower.tail = F)*2
    }else{
      pvalue <- pt(t,df)*2
    }
    if(pvalue < 0.05){
      cat("  t=",round(t,4)," ","df=",df," ","p-value=",round(pvalue,4),"\n"," Reject H0.")
    }else{
      cat("  t=",round(t,4)," ","df=",df," ","p-value=",round(pvalue,4),"\n"," Not reject H0")
    }
  }
}
```
## Let's test the effect of treatment on length at various days.
```{r, echo=TRUE}
rairuoho <- read.table("rairuoho.txt", header=T, sep="\t", dec='.')
```
### At day3, result shows t= -0.6474, p-value= 0.5206 > 0.05, so there is no significant difference between two treatments.
```{r, echo=TRUE}
my.t.test(rairuoho$day3,rairuoho$treatment)
```
### At day4, result shows t= 0.0387, p-value= 0.9693 > 0.05, so there is no significant difference between two treatments.
```{r, echo=TRUE}
my.t.test(rairuoho$day4,rairuoho$treatment)
```
### At day5, result shows t= 0.4499, p-value= 0.6549 > 0.05, so there is no significant difference between two treatments.
```{r, echo=TRUE}
my.t.test(rairuoho$day5,rairuoho$treatment)
```
### At day6, result shows t= 1.2043, p-value= 0.2346 > 0.05, so there is no significant difference between two treatments.
```{r, echo=TRUE}
my.t.test(rairuoho$day6,rairuoho$treatment)
```
### At day7, result shows t= 2.7786, p-value= 0.0079 < 0.05, so there is a significant difference between two treatments.
```{r, echo=TRUE}
my.t.test(rairuoho$day7,rairuoho$treatment)
```
### At day8, result shows t= 4.2038, p-value= 1e-04 < 0.05, so there is a significant difference between two treatments.
```{r, echo=TRUE}
my.t.test(rairuoho$day8,rairuoho$treatment)
```