---
title: "practice5.1"
author: "Ethan Wang"
date: "2022-10-21"
output: html_document
---

# In the practice5.1, I want to make a map featuring the global distribution of Manta birostris occurrence because manta ray is my favorite marine animal.
```{r,  eval=T, include=F}

library(leaflet)
library(rgbif)
library(tidyverse)
```
## First, I need to download the data of Manta birostris occurrence from GBIF website, and reform the gbif form into dataframe.
```{r,  eval=T}

gbif.manta <- occ_search(scientificName = "Manta birostris", limit = 1200) #Download 1200 records of Manta birostris occurrence.
gbif.manta.frame <- as.data.frame(gbif.manta$data) #The occurrence data I need is in gbif.manta$data, so transform it to dataframe.
gbif.manta.frame <- rename(gbif.manta.frame,latitude=decimalLatitude, longitude=decimalLongitude) #rename the columns.
```
## Next, I want to show the distribution on the ocean basemap.
```{r,  eval=T}

global.manta <- leaflet(gbif.manta.frame)%>%
  addProviderTiles(providers$Esri.OceanBasemap)%>% #Use the Esri.OceanBasemap
  addCircles(~longitude, ~latitude, popup = gbif.manta.frame) #Add circles to shoe the distribution
global.manta
```
## I also want to use different colors representing the years of the occurrence.
```{r,  eval=T}

lv.manta <- gbif.manta.frame$year%>%as.factor()
levels(lv.manta)
```
## As level(lv.manta) shows, these data are between 2010 and 2022, so I want to divide them into three groups.
```{r,  eval=T}

color.manta <- ifelse(gbif.manta.frame$year >=2010 & gbif.manta.frame$year<= 2013,"red",ifelse(gbif.manta.frame$year >= 2014 & gbif.manta.frame$year<= 2017,"green","blue")) #Data between 2010 and 2013 are red, between 2014 and 2017 are green, between 2018 and 2022 are blue.
lv.color.manta <- color.manta%>%as.factor() 
```
## Now, the data on the map are easy to see when they were recorded.
```{r,  eval=T}

global.manta <- global.manta%>%
  addCircles(~longitude, ~latitude, popup = gbif.manta.frame,  color = color.manta)%>% #Make different color
  addLegend("bottomright", colors = levels(lv.color.manta), labels = c("2010~2013","2014~2017","2018~2022"), title = "Years of global Manta birostris occurrence")%>% #Add the legend
  addMiniMap(tiles = "Esri.OceanBasemap") #Add the mini map
global.manta
```
## In addition, I found there is an organization,Pacific Research Foundation, located in Hawaii and dedicated to research of manta rays, so I want to add the popup of this foundation on the map.
```{r,  eval=T}

MPRF <- paste(sep = "<br/>", 
              "<b><a href='https://www.mantapacific.org/home'>Manta Pacific Research Foundation</a></b>",
              "Kailua-Kona, Hawaii  96745") #Make the information of popup
global.manta <- global.manta%>%addPopups(-155.0976410330908, 19.848274996428476, popup = MPRF, options = popupOptions(closeButton = T, closeOnClick = F)) #Add the popup on the map
```
## The final map I made is showed below.
```{r,  eval=T}

global.manta
```