---
title: "practice2.2"
output: html_document
date: "2022-09-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,  eval=T}

library(dplyr)
library(tidyr)
```

Read rairuoho.txt file.
```{r,  eval=T}

rairuoho <- read.table("rairuoho.txt", header=T, sep='\t', dec='.')
head(rairuoho)
```

Replace nutrient with enriched.
```{r,  eval=T}

nutrient <- rairuoho$treatment == "nutrient" #find "nutrient" in column of treatment
rairuoho[nutrient,"treatment"] <- "enriched" #replace "nutrient" with "enriched"
head(rairuoho)
```

Replace nutrient with enriched in the data set. Reformat the table in order to have the day as a single variable (factor) containing 6 levels.
Another variable length will be created to receive the length of the grass at the given day.
```{r,  eval=T}

rairuoho_day <- rairuoho%>%pivot_longer(day3:day8, names_to = "day", values_to = "length")
head(rairuoho_day)
```

Merge variables Spatial1 and Spatial2 in order to obtain the following format for the spatial coordinates of an observation upper_left.
```{r,  eval=T}

rairuoho_spatial <- rairuoho_day%>%mutate(spatial_coordinates=stringr::str_c(spatial1,spatial2, sep="_"))
head(rairuoho_spatial)
```

Remove variables spatial1, spatial, row and column.
```{r,  eval=T}

rairuoho_remove <- rairuoho_spatial%>%select(-spatial1,-spatial2,-row,-column)
head(rairuoho_remove)
```

```{r,  eval=T}

rairuoho_remove
```