---
title: "Practice3.2"
author: "Ethan Wang"
date: "2022-10-06"
output: html_document
---
# Practice3.2

```{r,  eval=T, include=F}

library(tidyverse)
```
### Create the following data frame from scratch.
```{r,  eval=T}

bubble_tea <- data.frame("before_diet"=c(104L,95L,87L,77L,112L), "after_diet"=c(96L,91L,81L,75L,118L), row.names = c("subject_1", "subject_2", "subject_3", "subject_4", "subject_5"))
bubble_tea
```
### Reformat this data frame to obtain the weight as a double into one column and the time of measurement as a factor with two levels before_diet and after_diet.
```{r,  eval=T}

bubble_tea$before_diet <- as.double(bubble_tea$before_diet) #convert integer to double
bubble_tea$after_diet <- as.double(bubble_tea$after_diet)
bubble_tea_long <- bubble_tea%>%pivot_longer(cols = everything(), names_to = "time_measurement", values_to = "weight") #reformat the data frame to obtain the weight into one column
bubble_tea_long <- as.data.frame(bubble_tea_long) #convert the tibble object to data frame
bubble_tea_long$time_measurement <- factor(bubble_tea_long$time_measurement, levels=c('before_diet','after_diet')) #convert time of measurement as factor with two levels
```
### Show the results 
```{r,  eval=T}

typeof(bubble_tea_long$weight) #the numeric type of weight is double
str(bubble_tea_long)
```
### Store this data frame as the first element of a list called BUBBLE_DIET.
```{r,  eval=T}

BUBBLE_TEA <- list(bubble_tea_long=bubble_tea_long)
str(BUBBLE_TEA)
```
### Create the second element of the list
```{r,  eval=T}

subject <- c(row.names(bubble_tea)) #a vector of character extracting the row names of the table previously created
weight_loss <- (bubble_tea$after_diet-bubble_tea$before_diet)/bubble_tea$before_diet*100 # a numeric vector (double) indicating the weight loss (in %) of each subject 
weight_loss_table <- data.frame(subject, weight_loss) #a combination of these two elements in a table with two columns: subject and weight_loss
```
### Show the results
```{r,  eval=T}

subject
weight_loss
weight_loss_table
```
### Create another list called WEIGHT_LOSS, storing the three elements.
```{r,  eval=T}

WEIGHT_LOSS <- list(subject=subject, weight_loss=weight_loss, weight_loss_table=weight_loss_table) #create another list
str(WEIGHT_LOSS)
```
### Put the list WEIGHT_LOSS into the list BUBBLE_TEA.
```{r,  eval=T}

BUBBLE_TEA[["WEIGHT_LOSS"]] <- WEIGHT_LOSS
str(BUBBLE_TEA)
```
### Create the third element of the list BUBBLE_TEA
```{r,  eval=T}

enjoyment_R <- 'Learning manipulating data in R is very difficult, but I enjoy the process.' #how much I enjoy manipulating data in R
BUBBLE_TEA[['enjoyment_R']] <- enjoyment_R #put enjoyment_R into the list BUBBLE_TEA 
```
## Show the results of practice3.2.
```{r,  eval=T}

str(BUBBLE_TEA)
```